---
title: "Syntax Highlighting"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      comment = "#>", collapse = TRUE)
source("utils.R")
```



R Markdown also comes with several built-in syntax highlighting styles. Supported styles include `r knitr::combine_words(rmarkdown:::html_highlighters(), before='\x60')`. Pass `null` to prevent syntax highlighting. To use a highlighter for a single .html file output from a .Rmd file, you edit your YAML:

```yaml
title: "README.Rmd"
output_format: 
  html_document:
    highlighter: tango
```

# Options gallery

```{r echo = FALSE}
hl_links <- link_factory(type = "highlighters")
#table_factory(links = hl_links)
```

```{r results = "asis", echo = FALSE}
hl_links %>% 
  select(contains("list", ignore.case = TRUE), contains("image_html")) %>% 
  gt::gt() %>% 
    gt::fmt_markdown(
      columns = everything()
    )
```

---

# My render script

And here is the script to generate the highlighters:

```{r echo = FALSE}
render_factory("highlighters")
```
