---
always_allow_html: yes
output:
  github_document:
    toc: true
---

Herein lies a `README` to help you navigate the galleries.

```{r include = FALSE}
library(fs)
library(kableExtra)
library(tidyverse)
root <- "https://apreshill.github.io/rmd-render-factory/"
```

# Themes

R Markdown comes with some several built-in `theme`s. Themes are drawn from the Bootswatch theme library. Valid themes include `r knitr::combine_words(rmarkdown:::themes(), before='\x60')`. Pass `null` for no theme. To use a theme for a single .html file output from a .Rmd file, you edit your YAML:

```yaml
title: "README.Rmd"
output_format: 
  html_document:
    theme: flatly
```

```{r}
themes <- dir_ls("gallery/themes", recursive = TRUE, glob = "*.html") %>% 
  enframe(name = "path", value = "junk") %>% 
  select(-junk) %>% 
  mutate(path = glue::glue("{root}{path}")) %>% 
  mutate(link_read = path %>% fs::path_file(.) %>% path_ext_remove(.) %>% as.character())
```

```{r make-gallery, results = 'asis'}
themes %>% 
  mutate(link = cell_spec(link_read, 
                           "html", 
                          link = path)
         ) %>% 
  select("Theme Gallery" = link) %>% 
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) 
```

```{r}
library(dplyr)
library(knitr)
library(kableExtra)
dt_url <- c("https://en.wikipedia.org/wiki/Cadillac_Fleetwood",
            "https://www.lincoln.com/luxury-cars/continental/",
            "http://shop.honda.com/civics.aspx",
            "https://bringatrailer.com/2011/12/28/striking-1973-maserati-bora-4-9/")

mtcars[c(15,16,19,31),1:3] %>% 
  mutate(model = cell_spec(row.names(.), "html", link = dt_url)) %>%
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) 
```



# Highlighters

R Markdown also comes with several built-in syntax highlighting styles. Supported styles include `r knitr::combine_words(rmarkdown:::html_highlighters(), before='\x60')`. Pass `null` to prevent syntax highlighting. To use a highlighter for a single .html file output from a .Rmd file, you edit your YAML:

```yaml
title: "README.Rmd"
output_format: 
  html_document:
    highlighter: tango
```

# Output formats
