---
always_allow_html: yes
output:
  github_document:
    toc: true
---

Herein lies a `README` to help you navigate the galleries.

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = NA)
library(tidyverse)
```

```{r factory_functions}
link_factory <- function(dir = "gallery", 
                         type = c("themes", "highlighters", "outputs", "viridis-options"),
                         root = "https://apreshill.github.io/rmd-render-factory/"){
  if(!missing(type) & length(type) > 1) stop("Only one 'type' allowed.")
  library(dplyr)
  type <- match.arg(type)
  html_dir <- fs::dir_ls(glue::glue("{dir}/{type}"), recursive = TRUE, glob = "*.html")
  html_items <- html_dir %>% 
    tibble::enframe(name = "rel_path", value = "junk") %>% 
    dplyr::select(-junk) %>% 
    dplyr::mutate(abs_path = glue::glue("{root}{rel_path}")) %>% 
    dplyr::mutate(label_path = rel_path %>% fs::path_file(.) %>% 
                  fs::path_ext_remove(.) %>% as.character(.)) %>% 
    dplyr::mutate(link = glue::glue("[{label_path}]({abs_path})")) %>% 
    dplyr::rename_at(vars(link), ~glue::glue("List of {type}")) %>% 
    dplyr::mutate(image_link = as.character(fs::dir_ls(path = "thumbnails", regexp = glue::glue("{type}")))) %>% 
    dplyr::mutate(image_md = glue::glue("![]({image_link})"))
  return(html_items)
}

#' this function takes a tibble of links from link_factory()
#' and converts to an html table
table_factory <- function(links){
  html_items <- links
  html_table <- html_items %>% 
    dplyr::select(-ends_with("_path"), -starts_with("image_")) %>% 
    gt::gt() %>% 
    gt::fmt_markdown(
      columns = contains("List")
      )
  return(html_table)
}

#' this function takes webshots of all (absolute) links
webshot_factory <- function(links){
  html_items <- links
  for_shots <- html_items %>% 
    mutate(type = fs::path_rel(rel_path, start = "gallery") %>% fs::path_dir(.))
  webshot::webshot(glue::glue("{for_shots$abs_path}"),
                   glue::glue("thumbnails/{for_shots$type}-{for_shots$label_path}.png"), 
                   cliprect = "viewport")
}

#' this function prints the contents of an R script in a readable code chunk "as is"
render_factory <- function(type = c("single", "themes", "highlighters", "outputs", "palettes")){
  type <- match.arg(type)
  script <- readLines(glue::glue("render_{type}.R"))
  cat(script, sep = "\n")
}
```

# The single file

All of the links below derive from a single R Markdown file titled `index.Rmd`. Here is the YAML:

```{r}
cat(readr::read_lines("index.Rmd", n_max = 11), sep = "\n")
```



# Themes

R Markdown comes with some several built-in `theme`s. Themes are drawn from the Bootswatch theme library. Valid themes include `r knitr::combine_words(rmarkdown:::themes(), before='\x60')`. Pass `null` for no theme. To use a theme for a single .html file output from a .Rmd file, you edit your YAML:

```yaml
title: "README.Rmd"
output_format: 
  html_document:
    theme: flatly
```


```{r}
theme_links <- link_factory(type = "themes")
table_factory(links = theme_links)
```


And here is the script to generate the themes:

```{r}
render_factory("themes")
```

# Highlighters

R Markdown also comes with several built-in syntax highlighting styles. Supported styles include `r knitr::combine_words(rmarkdown:::html_highlighters(), before='\x60')`. Pass `null` to prevent syntax highlighting. To use a highlighter for a single .html file output from a .Rmd file, you edit your YAML:

```yaml
title: "README.Rmd"
output_format: 
  html_document:
    highlighter: tango
```


```{r}
hl_links <- link_factory(type = "highlighters")
table_factory(links = hl_links)
```

And here is the script to generate the highlighters:

```{r}
render_factory("highlighters")
```

# Output formats 

```{r}
output_links <- link_factory(type = "outputs")
table_factory(links = output_links)
```

And here is the script to generate the outputs:

```{r}
render_factory("outputs")
```

# Viridis options

```{r}
viridis_links <- link_factory(type = "viridis-options")
table_factory(links = viridis_links)
```

And here is the script to generate the viridis palettes:

```{r}
render_factory("palettes")
```


```{r eval = FALSE}
webshot_factory(links = theme_links)
webshot_factory(links = hl_links)
webshot_factory(links = output_links)
webshot_factory(links = viridis_links)
```



```{r, results ="asis", include = FALSE}
fig_files <- fs::dir_ls(path = "thumbnails", regexp = "themes") 
cat(paste0("* ", fig_files, " ![](", fig_files, ")\n"))
```

```{r eval = FALSE, include = FALSE}
# works just for one
# saving here for posterity
themes <- dir_ls("gallery/themes", recursive = TRUE, glob = "*.html") %>% 
  enframe(name = "path", value = "junk") %>% 
  select(-junk) %>% 
  mutate(path = glue::glue("{root}{path}")) %>% 
  mutate(link_read = path %>% fs::path_file(.) %>% path_ext_remove(.) %>% as.character())

themes %>% 
  mutate(link = cell_spec(link_read, 
                           "html", 
                          link = path)
         ) %>% 
  select("Theme Gallery" = link) %>% 
  kable("html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed")) 

# testing out screenshots for thumbnails
webshot::webshot("https://apreshill.github.io/rmd-render-factory/gallery/themes/darkly.html", "themes-darkly.png", cliprect = "viewport")
```


